Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11 \footnote{Based on observations with HST-COS, program GO 13017, PI Heckman}

### 2017-01-27 Paper/Paper.tex
Accepted version

The galaxy treated in this study is Haro 11, a well-studied Blue Compact Galaxy
at low redshift ($z = 0.021$). Morphologically, it is dominated by three major
star-forming knots, called knot A, B and C respectively, following the
terminology of \citet{Vader1993} \citep[see also][ and
fig.~\ref{fig:apert}]{Kunth1998, Hayes2007}.  Knots B and C are both very strong
in H$\alpha$, revealing that they also are producing strong Ly$\alpha$ 
But while knot C is a strong
Ly$\alpha$ emitter, knot B is a strong absorber, indicating that the neutral ISM
properties along the line of sight to the two knots are quite different
\citep{Hayes2009,Ostlin2009}.  Its complex kinematics indicates that it is
undergoing a merger or major interaction event \citep{Ostlin2001, Ostlin2015,
James2014}. It is the first galaxy in the local Universe \textbf{reported} to leak LyC
\citep{Bergvall2006}. \textbf{The same dataset has since been re-analyzed by
\cite{Grimes2007} who concluded that there was no convincing evidence for LyC
escape; and since by \cite{Leitet2011} who report an escape fraction of $3.3 \pm
0.7 \%$ based on a newbackground modeling. In this work, we assume that some
radiation does escape, but it should be kept in mind that this result has been
disputed.} Since Ly$\alpha$ escape is favored 
by some of the same conditions which also allow LyC escape 
\citep[see e.g. ][]{Hayes2015, DijkstraRev, Leitet2011}, the leaking photons 
are assumed to originate from knot C, an assumption adopted in this work.

>>>>

The galaxy treated in this study is Haro 11, a well-studied Blue Compact Galaxy
at low redshift ($z = 0.021$). Morphologically, it is dominated by three major
star-forming knots, called knot A, B and C respectively, following the
terminology of \citet{Vader1993} \citep[see also][ and
fig.~\ref{fig:apert}]{Kunth1998, Hayes2007}.  Knots B and C are both very strong
in H$\alpha$, revealing that they also are producing strong Ly$\alpha$ 
But while knot C is a strong
Ly$\alpha$ emitter, knot B is a strong absorber, indicating that the neutral ISM
properties along the line of sight to the two knots are quite different
\citep{Hayes2009,Ostlin2009}.  Its complex kinematics indicates that it is
undergoing a merger or major interaction event \citep{Ostlin2001, Ostlin2015,
James2014}. It is the first galaxy in the local Universe reported to leak LyC
\citep{Bergvall2006}. The same dataset has since been re-analyzed by
\cite{Grimes2007} who concluded that there was no convincing evidence for LyC
escape; and since by \cite{Leitet2011} who report an escape fraction of $3.3 \pm
0.7 \%$ based on a new background modeling. In this work, we assume that some
radiation does escape, but it should be kept in mind that this result has been
disputed. Since Ly$\alpha$ escape is favored 
by some of the same conditions which also allow LyC escape 
\citep[see e.g. ][]{Hayes2015, DijkstraRev, Leitet2011}, the leaking photons 
are assumed to originate from knot C, an assumption adopted in this work.
